\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{purple} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% Avoid hyphenating words, paragraphs look a lot neater
\usepackage[none]{hyphenat}

\usepackage[scale=.80]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates
%column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to
%adjust the width of the space allocated to your name

% personal data
\name{Aishwarya Pant}{}
\address{London, United Kingdom}{}
\social[linkedin]{aishpant}
\social[twitter]{aishpant}
\social[github]{aishpant}
\email{aishpant@gmail.com}
\homepage{aishpant.dev}    
\extrainfo{Updated on \today}
    
\begin{document}

\makecvtitle

%----------------------------------------------------------------------------------------
%	ABOUT
%----------------------------------------------------------------------------------------


\section{About}
\cvitem{}{A strong individual contributor with experience in leading the design and implementation of technical features. I advocate for quality, testing and user experience.}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Work Experience}
\cventry{August 2018 - Present}{Backend Engineer}{\textsc{Monzo Bank Limited}}{}{London}{\textnormal{Monzo is an online bank with 4 million customers, where I work in a Financial Crime team responsible for automation of risky procedures.
\vspace{1mm}
\begin{itemize}
    \item Automated account defunds: \\
    Designed and implemented decision systems for determining if it is safe to automatically defund a blocked customers' account. Defunds are critical piece of infrastructure subject to complex regulation; correctness and robustness is essential. I wrote extensive unit tests and acceptance tests for validating the correctness and to make future refactors easier. Almost 50\% of all fincrime defunds were automated, which saved hundreds of hours per week in operational work. Till date, this system has moved over 2 million pounds.
    \vspace{1mm}
    \item Improved user experience for blocked users: \\
    Built a new extensible flow for customers whose accounts are temporarily blocked. This system was built to make it easy to view and debug the activity of a blocked user, and is expected to reduce complaints and inbound chats and calls.
    \vspace{1mm}
    \item Multi party authorisation: \\
    Added support for making manual account defunds asynchronous. It's a safety critical control that helps ensure that operations at Monzo are safe, meeting the high expectation of our customers and regulators.
\end{itemize}
\vspace{1mm}
 I also have experience of building APIs in product focused teams:
\vspace{1mm}
\begin{itemize}
    \item Built core banking features like financial account summary and payee accounts.
    \vspace{1mm}
    \item Collaborated with external partners to integrate energy switching, contents insurance and a remortgaging service within the Monzo app. Since its launch in 2019, energy switching has generated a revenue of over £500,000.
\end{itemize}
}}

\vspace{3mm}

\cventry{Dec 2017 --
March 2018}{Outreachy Intern}{\textsc{Linux
Kernel}}{}{Remote}{\textnormal{Outreachy is a three-month internship programme
to get more underrepresented people to work on Free \& Open Source Software
(FOSS). I wrote a library using python \& coccinelle scripts, to improve
attribute documentation for the Linux Kernel. This library - abi2doc is available on PyPI (\url{https://pypi.python.org/pypi/abi2doc}) and the code is on GitHub (\url{https://github.com/aishpant/attribute-documentation}).
\vspace{1mm}
\begin{itemize}
	\item I wrote an extended description of the project here - \url
		{https://aishpant.github.io/blog/attribute-documentation/}
		\vspace{1mm}
	\item A list of patches I have submitted to the Linux Kernel-
		\url{https://git.kernel.org/pub/scm/linux/kernel/git/next/linux-next.git/log/?qt=grep&q=Aishwarya+Pant}.
		\vspace{1mm}
        \item Using abi2doc, I added documentation for \textbf{312} sysfs attributes.
\end{itemize}
}}

\vspace{3mm}

\cventry{July 2015 - Nov 2017}{Software Development Engineer}{\textsc{Flipkart}}{}{Bengaluru}{\textnormal{Flipkart is one of the largest e-commerce companies in India, with 10 million monthly active users. I primarily worked in the supply chain division of Flipkart.
\vspace{1mm}
\begin{itemize}
	\item Highlights have
been building a user interface (based on  ReactJS) for use in transportation
hubs and writing a new sortation service (based on a Java Dropwizard
framework) for use in shipment sortation hubs.
\vspace{1mm}
        \item I also worked for 6 months with the Merchandisation
\& Monetisation team, onboarding new widgets on the landing \& category pages.
\end{itemize}
}}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{2011--2015}{Indraprastha Institute of Information Technology, Delhi \url{https://iiitd.ac.in/}}{B.Tech GPA 8.82}{}{\textit{Computer Science}}{}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\section{Programming}
\cvitem{}{\textnormal{Proficient in Go.}}
\cvitem{}{\textnormal{Comfortable with Python, Java, Coccinelle.}}

\section{Software}
\cvitem{}{\textnormal{SQL, NSQ, Cassandra, Prometheus, Linux, Git}}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\section{Publications}
\cventry{2015}{Understanding Thermal Face Detection: Challenges and
Evaluation}{\textsc{Book chapter in "Face Recognition Across the
Electromagnetic Spectrum"}}{}{}{\textnormal{Book Editor Thirimachos Bourlai,
Springer.
Authors: Janhavi Agrawal, Aishwarya Pant, Tejas Dhamecha, Richa Singh,
Mayank Vatsa}}

%----------------------------------------------------------------------------------------
%	TALKS, AWARDS
%----------------------------------------------------------------------------------------

\section{Talks and Awards}
\cvitem{}{Participated in Outreachy panel at Open Source Summit EU 2018}
\cvitem{}{Awarded scholarship to attend KubeCon + CloudNativeCon Europe 2018}

\end{document}

\end{document}

